Concrete Semantics for Pushdown Analysis:\\The Essence of Summarization

### 2013-10-02 content.tex
Added code to describe the math of touches-kont. Fixed circularity fix.

\begin{mathpar}
  \inferrule{ }{\kmt \in \unroll{\mktab}{\kmt, G}} \quad
  \inferrule{\mkont \in \unroll{\mktab}{\mkont', \bot}}{\mkframe:\mkont \in \unroll{\mktab}{\mkframe:\mkont', G}} \\
  \inferrule{G \neq \mctx \\
             \mkont^\circ \in \mktab(\mctx) \\
             \mkont \in \unroll{\mktab}{\mkont^\circ, \mctx}}
            {\mkont \in \unroll{\mktab}{\krt{\mctx}, G}}  
\end{mathpar}
Consider later uses of $\mathit{unroll}$ to implicitly give $\bot$ for $G$.

@@

@@

>>>>

\begin{mathpar}
  \inferrule{ }{\kmt \in \unroll{\mktab}{\kmt, G}} \quad
  \inferrule{\mkont \in \unroll{\mktab}{\mkont', G}}{\mkframe:\mkont \in \unroll{\mktab}{\mkframe:\mkont', G}} \\
  \inferrule{\mctx \notin G  \\
             \mkont^\circ \in \mktab(\mctx) \\
             \mkont \in \unroll{\mktab}{\mkont^\circ, \set{\mctx}\cup G}}
            {\mkont \in \unroll{\mktab}{\krt{\mctx}, G}}  
\end{mathpar}
Consider later uses of $\mathit{unroll}$ to implicitly give $\emptyset$ for $G$.

@@

The first is that the memo table only contains information about previously seen contexts; we need this to infer that there was at least one call leading to the memoized context such that we can use stack irrelevance to justify skipping to the memoized result.
%
The second (the existential clause) states that all the calling contexts in the continuation table reach some unrolling of the current state.
%
The final invariant states that the memo table is correct: all calling contexts reach the memoized result, with well-bracketing.

@@

An implementation of the same functionality would use a mutable set to track which contexts have been traversed to build up a set of addresses:
% This code is typeset below by Scribble
% \begin{lstlisting}[mathescape]
% (define (touch-kont $\mkont$ $\mktab$)
%   (define seen (mutable-seteq))
%   (let loop ([$\mkont$ $\mkont$])
%     (match $\mkont$
%       [(mt) $\emptyset$]
%       [(cons $\mkframe$ $\mkont$) ($\cup$ $\touchesf(\mkframe)$ (loop $\mkont$))]
%       [(rt $\mctx$)
%        (cond
%          [(set-member? seen $\mctx$) $\emptyset$]
%          [else
%           (set-add! seen $\mctx$)
%           (for/union ([$\mkont$ (in-set $\mktab(\mctx)$)]) (loop $\mkont$))])])))           
% \end{lstlisting}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Begin scary Scribble output
\newcommand{\SCodePreSkip}{\vskip\abovedisplayskip}
\newcommand{\SCodePostSkip}{\vskip\belowdisplayskip}
\newenvironment{SCodeFlow}{\SCodePreSkip\begin{list}{}{\topsep=0pt\partopsep=0pt%
\listparindent=0pt\itemindent=0pt\labelwidth=0pt\leftmargin=2ex\rightmargin=2ex%
\itemsep=0pt\parsep=0pt}\item}{\end{list}\SCodePostSkip}
\newenvironment{SingleColumn}{\begin{list}{}{\topsep=0pt\partopsep=0pt%
\listparindent=0pt\itemindent=0pt\labelwidth=0pt\leftmargin=0pt\rightmargin=0pt%
\itemsep=0pt\parsep=0pt}\item}{\end{list}}
\newenvironment{RktBlk}{}{}
\definecolor{IdentifierColor}{rgb}{0.15,0.15,0.50}
\definecolor{ParenColor}{rgb}{0.52,0.24,0.14}
\newcommand{\RktSym}[1]{\inColor{IdentifierColor}{#1}}
\newcommand{\RktPn}[1]{\inColor{ParenColor}{#1}}

\begin{SCodeFlow}\begin{RktBlk}\begin{SingleColumn}\RktPn{(}\RktSym{define}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{touch{-}kont}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{$\mkont$}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{$\mktab$}\RktPn{)}

\mbox{\hphantom{\Scribtexttt{xx}}}\RktPn{(}\RktSym{define}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{seen}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{mutable{-}seteq}\RktPn{)}\RktPn{)}

\mbox{\hphantom{\Scribtexttt{xx}}}\RktPn{(}\RktSym{let}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{loop}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktPn{[}\RktSym{$\mkont$}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{$\mkont$}\RktPn{]}\RktPn{)}

\mbox{\hphantom{\Scribtexttt{xxxx}}}\RktPn{(}\RktSym{match}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{$\mkont$}

\mbox{\hphantom{\Scribtexttt{xxxxxx}}}\RktPn{[}\RktPn{(}\RktSym{mt}\RktPn{)}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{$\emptyset$}\RktPn{]}

\mbox{\hphantom{\Scribtexttt{xxxxxx}}}\RktPn{[}\RktPn{(}\RktSym{cons}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{$\mkframe$}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{$\mkont$}\RktPn{)}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{$\cup$}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{touches{-}frame}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{$\mkframe$}\RktPn{)}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{loop}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{$\mkont$}\RktPn{)}\RktPn{)}\RktPn{]}

\mbox{\hphantom{\Scribtexttt{xxxxxx}}}\RktPn{[}\RktPn{(}\RktSym{rt}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{ctx}\RktPn{)}

\mbox{\hphantom{\Scribtexttt{xxxxxxx}}}\RktPn{(}\RktSym{cond}

\mbox{\hphantom{\Scribtexttt{xxxxxxxx}}}\RktPn{[}\RktPn{(}\RktSym{set{-}member{\hbox{\texttt{?}}}}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{seen}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{ctx}\RktPn{)}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{$\emptyset$}\RktPn{]}

\mbox{\hphantom{\Scribtexttt{xxxxxxxx}}}\RktPn{[}\RktSym{else}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{set{-}add{\hbox{\texttt{!}}}}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{seen}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{ctx}\RktPn{)}

\mbox{\hphantom{\Scribtexttt{xxxxxxxxxxxxxx}}}\RktPn{(}\RktSym{for/union}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktPn{[}\RktSym{$\mkont$}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{in{-}set}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{dict{-}ref}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{$\mktab$}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{ctx}\RktPn{)}\RktPn{)}\RktPn{]}\RktPn{)}

\mbox{\hphantom{\Scribtexttt{xxxxxxxxxxxxxxxx}}}\RktPn{(}\RktSym{loop}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{$\mkont$}\RktPn{)}\RktPn{)}\RktPn{]}\RktPn{)}\RktPn{]}\RktPn{)}\RktPn{)}\RktPn{)}\end{SingleColumn}\end{RktBlk}\end{SCodeFlow}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% End of scary Scribble output
